ggalluvial: Layered Grammar for Alluvial Plots

### 2019-12-05 paper.rmd
try to rm figure caption 2

```{r figure, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6, fig.cap=NA}
library(ggalluvial)
combos <- data.frame(
  stat = c(
    rep("stratum", 2),
    rep("alluvium", 4),
    "flow",
    # text geom
    c("stratum", "alluvium", "flow"),
    # errorbar and pointrange geoms
    "stratum", "alluvium", "flow"
  ),
  geom = c(
    c("stratum", "lode"),
    c("stratum", "alluvium", "lode", "flow"),
    "flow",
    rep("text", 3),
    "errorbar", "pointrange", "pointrange"
  ),
  pairing = c(
    c("default", "alluvial"),
    c("alluvial", "default", "default", "alluvial"),
    "default",
    rep("external", 6)
  )
)
levs <- c("stratum", "alluvium", "lode", "flow",
          "text", "errorbar", "pointrange")
combos <- transform(
  combos,
  stat = factor(stat, levs),
  geom = factor(geom, levs),
  pairing = factor(pairing, c("default", "alluvial", "external"))
)
ggplot(combos, aes(axis1 = stat, axis2 = geom)) +
  scale_x_discrete(limits = c("stat", "geom"), expand = c(.1, .05)) +
  geom_alluvium(aes(fill = pairing)) +
  scale_fill_brewer(type = "qual") +
  geom_stratum() +
  geom_text(stat = "stratum", infer.label = TRUE) +
  theme_minimal()
```

>>>>

```{r figure, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6, fig.cap=""}
library(ggalluvial)
combos <- data.frame(
  stat = c(
    rep("stratum", 2),
    rep("alluvium", 4),
    "flow",
    # text geom
    c("stratum", "alluvium", "flow"),
    # errorbar and pointrange geoms
    "stratum", "alluvium", "flow"
  ),
  geom = c(
    c("stratum", "lode"),
    c("stratum", "alluvium", "lode", "flow"),
    "flow",
    rep("text", 3),
    "errorbar", "pointrange", "pointrange"
  ),
  pairing = c(
    c("default", "alluvial"),
    c("alluvial", "default", "default", "alluvial"),
    "default",
    rep("external", 6)
  )
)
levs <- c("stratum", "alluvium", "lode", "flow",
          "text", "errorbar", "pointrange")
combos <- transform(
  combos,
  stat = factor(stat, levs),
  geom = factor(geom, levs),
  pairing = factor(pairing, c("default", "alluvial", "external"))
)
ggplot(combos, aes(axis1 = stat, axis2 = geom)) +
  scale_x_discrete(limits = c("stat", "geom"), expand = c(.1, .05)) +
  geom_alluvium(aes(fill = pairing)) +
  scale_fill_brewer(type = "qual") +
  geom_stratum() +
  geom_text(stat = "stratum", infer.label = TRUE) +
  theme_minimal()
```
